%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{Carolina}{Jiménez Gómez}
       {}


% In the aside, each new line forces a line break
\begin{aside}
  \section{About}
    Colombian.
    ~
    \href{mailto:carolina.jimenez.g@gmail.com}{carolina.jimenez.g@
    gmail.com}
    \href{https://github.com/carolinajimenez26}{github.com/
    carolinajimenez26}
    \href{https://carolinajimenez26.github.io/}{personal web page}
  \section{Languages}
    Spanish (Native), English (Good)
  \section{Skills}
    {\color{red} $\varheartsuit$} JavaScript, Node.js,
    Python, C++, git/GitHub, Linux, SQL, mongoDB,
    CSS \& HTML, React Native
\end{aside}

\section{Work Experience}

\begin{entrylist}

    \entry
    {2018}
    {\href{https://www.digitalproductschool.io/index}{Digital Product School}}
    {Software Engineer}
    {\emph{Worked in a diverse team consisting in Software Engineers, Product Managers, Interaction Designer and  AI Engineer. The goal of our team was to make Trcuk Driving more attractive and to build a Software prototype in only 3 months.
    A mobile application was developed which allows truck drivers to communicate with each other. React Native and Firebase were used.
    }}
    
    \entry
    {2017 - 2018}
    {\href{http://judge.utp.edu.co/}{Sirius Research Group}}
    {Undergraduate Researcher.}
    {\emph{
    Researched about tractographies, including comparisons between different tools to generate them, comparisons between different tractography's algorithms and selection of the MRtrix tool with global tractography algorithm; a test software was developed that automates the processes for tractography generation. A web page was created with Django as a backend and Bootstrap for the frontend.
    }}
    
  \entry
    {2015 - 2017}
    {\href{http://judge.utp.edu.co/}{Sirius Research Group}}
    {Research Assistant.}
    {\emph{Research Assistant in digital image processing in neuro-computation and web development.
    Construction of a web page with Node.js, HTML/CSS, Materialize and JavaScript for calculation of brain densitometries. Some packages of Python for neurocomputing were used.
    }}
    
    \entry
    {since 2013}
    {\href{http://github.com/carolinajimenez26}{Personal and University Projects}}
    {}
    {\emph{Projects of: SQL and No-SQL databases, web development, programming, parallel programming, among others. You can see most of them at \textbf{\href{http://github.com/carolinajimenez26}{my GitHub}}.
    }}

    
\end{entrylist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Volunteer Experience}

\begin{entrylist}

\entry
    {2016}
    {\href{https://github.com/jointDeveloper/jointdeveloper.github.io}{jointDeveloper - Web}}
    {Front-end Developer}
    {\emph{Colaborator of the first implementation of the website for jointDeveloper with the use of HTML / CSS and Javascript.}}
    
    
\entry
    {since 2015}
    {\href{https://sirius.utp.edu.co/jointdeveloper/}{jointDeveloper}}
    {Co-Founder}
    {\emph{Co-founder, mentor and speaker. Comunity and seedbed that seeks to generate interest in the areas of programming and technology in women. Programming and technology teaching. 
    }}
    
\end{entrylist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\clearpage

\section{Awards}

\begin{entrylist}
    \entry
    {2017}
    {Grace Hopper Celebration Scholar}
    {\href{https://ghc.anitab.org/}{AnitaB.org}}
    {\emph{\textit{"The Grace Hopper Celebration is the world's largest gathering of women technologists."} 
    October 4 to 6, Orlando - Florida}}
\end{entrylist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\begin{entrylist}
  \entry
    {2013 - 2018}
    {BSc {\normalfont System and Computer Engineering}}
    {\href{http://www.utp.edu.co/}{Universidad Tecnlógica de Pereira}}
    {\emph{Distinguished student, 4.3/5 GPA}}
\end{entrylist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications}

\begin{entrylist}

    \entry
    {2017}
    {Poster Speaker in Seventh Departamental Meeting of Risaralda Research Seeds}
    {\href{http://www.rredsi.co/}{RREDSI}}
    {\emph{Poster title: \textit{"Calculation of brain densities to determine the cause of death of patients who have suffered head injuries"}.}}
    
    \entry
    {2016}
    {Certificate in \textit{Scientific Computing, Simulation and Big Data}}
    {\href{http://bios.org.co/es-es/}{BIOS}}
    {\emph{At {\href{http://www.utp.edu.co/}{Universidad Tecnlógica de Pereira}} with a duration of 120 hours.}}
    
\end{entrylist}

% \section{Interests}

% Software Development, Programming, Research, Neurocomputation, Web Development.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



% \section{selected coursework}


%     $\bullet$ Data structures and algorithms. $\bullet$ Computer programming paradigms. $\bullet$ Information technology introduction and Logics. $\bullet$ Courses on computer programming that cover the imperative, functional and object-oriented paradigms, parallel programming.
%     $\bullet$ three courses on mathematics, three on physics, two on statistics and one on linear algebra. $\bullet$ Computer architecture $\bullet$ Electronics $\bullet$ Compilers $\bullet$ Databases $\bullet$ Artificial intelligence $\bullet$ Soft Computing.



% \section{references}

% \begin{itemize}
%     \item \textbf{John Haiber Osorio}. 
%     Teacher at \href{http://www.utp.edu.co/}{Universidad Tecnlógica de Pereira}. 
%     Cell phone: +57 3113018021.  
%     email: \href{mailto:jhosorio@utp.edu.co}{jhosorio@utp.edu.co}.
%     \item \textbf{Yensy Helena Gómez}.
%     Teacher at \href{http://www.utp.edu.co/}{Universidad Tecnlógica de Pereira}. 
%     Cell phone: +57 3172145026.  
%     email: \href{mailto:yensy@sirius.utp.edu.co}{yensy@sirius.utp.edu.co}.
% \end{itemize}



% \section{publications}

% Put your publications here!

%%% This piece of code has been commented by Karol Kozioł due to biblatex errors. 
% 
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\end{document}
